---
title: "Sentinel-3"
subtitle: "Pioneering Earth Observation for Europe"
author: "Muhan Yang"
institute: "CASA, UCL"
date: "18/01/2024 (updated: 2023-01-27)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-all, echo=FALSE}
#library(countdown)
library(xaringan)
#library(xaringanExtra)
library(knitr)

hook_source <- knitr::knit_hooks$get('source')
knitr::knit_hooks$set(source = function(x, options) {
  x <- stringr::str_replace(x, "^[[:blank:]]?([^*].+?)[[:blank:]]*#<<[[:blank:]]*$", "*\\1")
  hook_source(x, options)
})

xaringanExtra::use_tachyons()
xaringanExtra::use_broadcast()
xaringanExtra::use_freezeframe()
xaringanExtra::use_scribble()
xaringanExtra::use_slide_tone()
xaringanExtra::use_search(show_icon = TRUE, auto_search = FALSE)
xaringanExtra::use_freezeframe()
xaringanExtra::use_clipboard()
xaringanExtra::use_tile_view()
xaringanExtra::use_panelset()
xaringanExtra::use_editable(expires = 1)
xaringanExtra::use_fit_screen()
xaringanExtra::use_extra_styles(
  hover_code_line = TRUE,         
  mute_unhighlighted_code = TRUE  
)

```

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(fontawesome)
```

```{r, echo=FALSE}
xaringanExtra::use_progress_bar(color = "#0051BA", location = "bottom")
```

### Overview
- **Bullet Points**:
  - "A cornerstone of the Copernicus Programme, dedicated to Earth's environmental monitoring."
  - "Comprising two identical satellites, Sentinel-3A and Sentinel-3B, for optimal coverage and data delivery."
  - "Focus areas: oceans, land, ice, and atmosphere monitoring for a healthier planet."

---

### Composition
- **Bullet Points**:
  - "Dual satellites launched in 2016 (Sentinel-3A) and 2018 (Sentinel-3B) to ensure continuous data."
  - "Key Instruments: OLCI, SLSTR, and SRAL - each serving a unique purpose in Earth observation."
  - "Orbiting 814 km above Earth, providing global coverage every 1 to 2 days."
  
---

### Key Sensors and Their Functions
- **OLCI**:
  - "Captures high-resolution color imagery."
  - "Monitors ocean health and productivity, vegetation, and river water color."
- **SLSTR**:
  - "Measures global temperature changes with accuracy."
  - "Key for climate change research and natural disaster monitoring."
- **SRAL**:
  - "Provides precise altitude measurements."
  - "Critical for sea level monitoring and ice thickness assessment."
  
---

### Application Cases
- **Oceanography**:
  - "Tracks chlorophyll concentration, supporting sustainable fisheries management."
- **Climate Change**:
  - "Monitors ice melting patterns and sea-level rise, contributing to climate models."
- **Environmental Monitoring**:
  - "Assesses changes in land use, forest monitoring, and wildfire damage."
- **Disaster Management**:
  - "Supports rapid response with accurate data on floods, oil spills, and other emergencies."
  
---

### Data Usage and Access
- **Bullet Points**:
  - "Sentinel-3 data is freely available via the Copernicus Open Access Hub, supporting researchers, policymakers, and the public."
  - "Examples of use cases include tracking urban expansion, agricultural productivity, and environmental protection efforts."
  - "Resources for data processing include SNAP (Sentinel Application Platform) and various ESA tutorials."
  
---

### Contributions and Future of Sentinel-3
- **Bullet Points**:
  - "A pivotal role in understanding and responding to climate change."
  - "Future plans include enhancing instrument capabilities and data accuracy."
  - "Continued collaboration with international partners to expand Earth observation efforts."
  
---
### Reflection
---

### Conclusion and Resources
- **Summary**:
  - "Sentinel-3 stands as a testament to the power of Earth observation for a sustainable future."
- **Resources**:
  - "For more information, visit [ESA's Sentinel-3 webpage](#) and [Copernicus Open Access Hub](#)."
- **Acknowledgments**:
  - "Thank you to the European Space Agency and Copernicus for their ongoing commitment to Earth observation."





